### 2023-01-19 code/1_exclusions/1_exclusionsUS.Rmd
small changes based on Mike's feedback

```{r}
write.csv(df.resp_E, "../../data/responding/dataUS_excl.csv")
```

>>>>

```{r}

df.demog_metadata <- data.frame(ppts_finished = c(length(unique(df.ppts_finished_E$subject))),
                      ppts_after_att_check_excl = c(length(unique(df.ppts_att_E$subject))),
                      ppts_non_native_speaker = c(length(ppts_non_native_lang_E)), 
                      ppts_vi_speaker_E = c(length(ppts_vi_speaker_E)), 
                      ppts_zh_speaker_E = c(length(ppts_zh_speaker_E)), 
                      ppts_lived_abroad_E = c(length(ppts_lived_abroad_E)), 
                      ppts_oversea_exp_E = c(length(ppts_oversea_exp_E)),

                      ppts_after_demog_excl = c(length(unique(df.resp_E$subject))))
colnames(df.demog_metadata) <- c("Participants Finished", 
                                 "Participants ")
```

```{r}
write.csv(df.resp_E, "../../data/responding/dataUS_excl.csv")
write.csv(df.demog_metadata, "../../data/responding/dataUS_excl_metadata.csv")
```
